### 2013-11-26 PositionPaper/incremental.tex
Incrementar et use case

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results. The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated. 
The following sections describe how this query is computed according to our approach.

@@

The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs that leads to a {\em derived SLA} that guides the evaluation of a query. A query has associated preferences  expressed as macroscopic constraints: execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode. These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assined storage space, number of requests, transfered Mega Octets, etc.). Given a query and its preferences statement, the system  finds relevant service compositions that produces results  such that when combined, they meet the required constraints.

@@

We assume that services export SLA's (i.e., agreed SLA's) that define measures  of finer granularity than those defined by the user.  The service SLA measures  are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request. These measures are in general computed by monitoring the execution and conversations associted to services. For example the cost of retrieving the list of energy providers within a region with their KWatt cost provided that calls cost between 0,25 - 0,50 euros depending on the data service. This request  includes the price of calling a service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network. Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
 Measures can be also hybrid, in the sense that they can be statically stated partially but they require to be precised at execution time.  A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

@@

 We propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA is can be seen as a set of equations that has to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

>>>>

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA derivation computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results. The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated. 
The following sections describe how this query is computed according to our approach.

@@

The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs. This  leads to a {\em derived SLA} that guides the evaluation of a query. A query has associated preferences  expressed as macroscopic constraints (i.e. user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode. These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.). Given a query and its preferences statement, the system  finds  service compositions that produce results   meeting the required constraints.

@@

We assume that services export SLAs (i.e., agreed SLAs) that define measures  of finer granularity than those defined by the user.  The service SLA measures  are: response time, availability, price/call, reliability, data production rate. Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request. These measures are, in general, computed by monitoring the execution and conversations associted to services. For example the cost of retrieving the list of energy providers within a region with their KWatt cost provided that calls cost between 0,25 - 0,50 euros depending on the data service. This request  includes the price of calling a service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network. Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
 Measures can be also hybrid, in the sense that they can be statically stated partially but they require to be precised at execution time.  A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

@@

 We propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. It specifies also how to compute coarse grained measures with fine grained ones. For example, data precision will be computed as a function of availability, freshness and provenance exported by data services. The derived SLA  can be seen as a set of inequations that have to be solved during the execution of a service composition. Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated. We will discuss this issue in the next sections.

### 2013-11-26 PositionPaper/useCase.tex
examples
Incremental (SLA) + figure in Use Case
Stabilizing section 3 ... a less abstract idea on how to deal with agreed and global SLA
Incrementar et use case

\begin{figure*}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure*}

@@

Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
Producers are characterized according to their location, the amount of energy in kWatts-hour that they can sell, the cost, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance. 
Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy. 
A energy exchange market is established in order to continuously monitor energy provision/consumption ensuring that all consumers will have the energy they require at every moment.

\begin{figure*}
\includegraphics[width=0.6\textwidth]{figs/arch.png}
\caption{\label{fig:energyXChange} Energy exchange.}
\end{figure*}

In our approach energy producers are modelled as services with associated ``agreed'' SLAs for a given time window. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific QoS preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.

\begin{itemize}
\item Processing big data implied in the energy consumption observation 
\item Computing energy consumption behavior models
\item Analyse and optimize energy consumption versus respecting the comfort requirement of inhabitants
\end{itemize}

Need of efficient data processing solutions

>>>>

\begin{figure*}
\includegraphics[width=0.8\textwidth]{figs/arch.png}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure*}

@@

Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
Producers are characterized according to their location, the amount of energy in kWatts-hour that they can sell, the cost, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance. 
Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy. 
A energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.

\begin{figure*}
\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
\caption{\label{fig:energyXChange} Energy exchange.}
\end{figure*}

In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. In our example assume that there are several energy provision services (e$_1$, ... e$_n$) that can be independent or hubs:
\begin{description}
\item energyProvider.requestAvailability() $\rangle$ $<$ KWatt/h, cost, rate, location $>$ $\langle$

\item energyHub.requestAvailability() $\rangle$ $<$ {ID, KWatt/h, cost, rate, location $>$}$\langle$
\end{description}
